---
title: "R Project 1 - Hello R"
author: "Victoria Le"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The variables included in the data frame are "dataset", "x", and "y".

### Exercise 2

The dino dataset plotted onto a graph:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation coefficient between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

The star dataset plotted onto a graph:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation coefficient between `x` and `y` in this dataset:

```{r cor-star}
star_data %>% 
  summarize(r = cor(x,y))
```

The correlation coefficient for the dino dataset is less and more negative than the star dataset correlation coeeficient. Both datasets have very weak negative correlations, but the dino dataset has a "stronger" negative correlation than the star dataset.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
```

```{r}
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)