---
title: "R Project 1 - Hello R"
author: "Victoria Le"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The variables included in the data frame are "dataset", "x", and "y".

### Exercise 2

The dino dataset plotted onto a graph:

```{r plot-dino, fig.width=10}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation coefficient between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

The star dataset plotted onto a graph:

```{r plot-star, fig.width=10}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation coefficient between `x` and `y` in this dataset:

```{r cor-star}
star_data %>% 
  summarize(r = cor(x,y))
```

The correlation coefficient for the dino dataset is less and more negative than the star dataset correlation coefficient. Both datasets have very weak negative correlations, but the dino dataset has a "stronger" negative correlation than the star dataset.

### Exercise 4

The circle dataset plotted onto a graph:

```{r plot-circle, fig.width=10}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
The correlation coefficient between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient for the circle dataset is less and more negative than the dino dataset correlation coefficient. Both datasets have very weak negative correlations, but the circle dataset has a "stronger" negative correlation than the dino dataset.

### Exercise 5

All of the plotted datasets and their summary correlation coefficients

```{r Datasets/Correlation Coefficients, fig.height=20, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
  